---
title: "Assignment 2"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For this Assignment, you will use the attached dataset. The goal of this assignment is to practice visualization tools in R. 


```{r}

library(ggplot2)
library(plyr)
library(foreach)

```

1. Load the data as a data frame. (1 point)
```{r}

data <- read.csv("Top50Movies.csv")

sub_data  = data[,c(3,4,5,8,9,10)]

transormData = function(col_data){
  col_data = as.array(col_data)
  new_col_data = aaply(.data = col_data, .margins = c(1), .fun = function(value){
    value = gsub("[,]","", value )
    value = gsub("[--]",NA, value )
    value = as.numeric(value)
  })
}

budgetInfAdj = transormData(col_data = sub_data$Budget..Inflation.Adjusted.Millions...)
worldInfAdj = transormData(col_data = sub_data$World.Box.Office.Receipts..Inflation.Adjusted.Millions...)
usInfAdj = transormData(col_data = sub_data$U.S..Box.Office.Receipts..Inflation.Adjusted.Millions...)
budgetNonInfAdj = transormData(col_data = sub_data$Budget..Non.Inflation.Adjusted.Millions...)
worldNonInfAdj = transormData(col_data = sub_data$World.Box.Office.Receipts..Non.Inflation.Adjusted.Millions...)
usNonInfAdj = transormData(col_data = sub_data$U.S..Box.Office.Receipts..Non.Inflation.Adjusted.Millions...)

keep <- names(data)
keep <- keep[-c(3,4,5,8,9,10)]
new_data <- subset(data, select = keep)
new_data = cbind(new_data, budgetInfAdj, worldInfAdj, usInfAdj, budgetNonInfAdj, worldNonInfAdj, usNonInfAdj)
new_data
```

2. Explore the relationship between the year released and inflation-adjusted U.S. box office receipts. Which plotting tool should you use for this purpose? Explain your findings. (2 points)

```{r}
ggplot(data = data, mapping = aes(x = Year.Released, y = usInfAdj)) +
  geom_line(na.rm = TRUE) +
  labs(title="Line Graph", x="Year Released", y="U.S. Box Office Receipts (Inflation Adjusted) ")

```

3. Explore the relationship between noninflation-adjusted budget and noninflation-adjusted world box office receipts. Explain your findings. (2 points)
```{r}
ggplot(data = data, mapping = aes(x = budgetNonInfAdj, y = worldNonInfAdj)) +
  geom_line(na.rm = TRUE) +
  labs(title="Line Graph", x="Non-Inflation Adjusted Budget", y="Non-Inflation Adjusted World Box Office Receipts")
```

4. Explore the relationship between inflation-adjusted budget and inflation-adjusted world box office receipts. Explain your findings. (2 points)
```{r}
ggplot(data = data, mapping = aes(x = budgetInfAdj, y = worldInfAdj)) +
  geom_line(na.rm = TRUE) +
  labs(title="Line Graph", x="Inflation Adjusted Budget", y="Inflation Adjusted World Box Office Receipts")
```
5. Use a proper plotting tool to how the distribution of inflation-adjusted U.S. box office receipts. (2 points)
```{r}
ggplot(data = data, mapping = aes(x = usInfAdj)) +
  geom_histogram(na.rm = TRUE, binwidth = 20) +
  labs(title="Line Graph", x="Inflation Adjusted U.S. Box Office Receipts")

```
6. Compare U.S. Box Office Receipts from each decade. Which plotting tool can be used here? Explain your findings. ( 2 points)
```{r}

```
7. Show the temporal pattern of U.S. Box Office Receipts. Which plotting tool can be used here. Explain your findings. (2 points)
```{r}

```
8. Explore the data yourself. Share an interesting finding that has not been explored above. (2 points)
```{r}

```